---
title: 'Presentation: Visualize CLT'
author: "Jun Yitt, Cheah"
date: "April 16, 2017"
output: ioslides_presentation
runtime: shiny
---

## Overview

This presentation, together with the shiny app were developed for the Developing Data Products Course Project.

The shiny app with documentation can be found here:
<https://jycheah.shinyapps.io/central_limit_theorem/>

Code for ui.R and server.R can be found here:
<https://github.com/junyitt/clt>


## Motivation
Consider we want to estimate the population mean of a uniform/exponential random variable.   
 
To estimate the population mean, we can carry out simulations and apply the Central Limit Theorem.

## Example
Consider the case where we want to estimate the population mean of an exponentially distributed random variable with lambda = 1.  
   
We could first simulate a sample of 50 random exponentials and take the mean.  
   
Then, we repeat this procedure 100,000 times to create the sample mean distribution.  
  

```{r}
   samples <- sapply(1:100000, FUN = function(x){
                  mean( rexp(50, rate = 1) )
        })

```

## Histogram
The population mean estimates should be centered around the sample mean distribution. 
```{r, fig.height= 3, echo = F}
hist(samples, breaks = 50, main = "Histogram of Sample Means", xlab = "Sample Means")
abline(v = mean(samples), col = "red", cex = 1.5)
m <- mean(samples)
```
Hence, the population mean is approximately `r m`. 
  
If you're interested to interactively simulate and visualize the effect of Central Limit Theorem, do check out my shiny app once again at:
<https://jycheah.shinyapps.io/central_limit_theorem/>  
Enjoy!


